\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
add captions to flow images.

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf} 
		\caption{old flow} 
	\label{fig:old-flow}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
		\caption{new flow} 
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf} 
		\caption{The current configuration interface has six screens. The first screen (F), bridge 
		question screen (B1), bridge configuration screen (B2), proxy question screen (P1), proxy configuration
		screen (P2), and a progress bar (Pr). If users answer yes to questions on B1 and P1, the 
		interface deems that they do need to configure a bridge or proxy and direct users to B2 and P2, respectively. 
		If they answer no, the interface deems that they do not need to configure a bridge or proxy and 
		they are directed to P1, Pr, respectively.}
	\label{fig:old-flow}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
		\caption{The redesigned configuration interface has five screens. The first screen (F), proxy configuration
		screen (P), a bridge configuration screen (B), summary screen (S), and a progress bar (Pr). The proxy 
		screen detects the need for a proxy and tells participants if they need to configure one, eliminating the need
		for a proxy question. The bridge configuration screen has the option to not configure a bridge, which 
		eliminates the need for a bridge question screen.} 
\end{figure*}
